---
title: "Using the xkcd pakcage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the xkcd pakcage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Browsing xkcd Comics

The main function of the xkcd package is to let you browse xkcd comics from within R. Let's see how we can accomplish this. First, load the `xkcd` package.

```{r setup}
library(xkcd)
```

Then, use the `xkcd()` function to retrieve information about a particular comic. We'll retrieve information about the first xkcd comic, so we'll set the argument equal to 1. 

```{r}
comic <- xkcd(number = 1)
```

The objects returned by the `xkcd()` function are special lists that belong to the xkcd class. This is useful becuase they can be provided directly to the `plot()` function in order to displace the comic. 

```{r}
plot(comic)
```

## Comic Data

The xkcd package also comes with a built-in dataset describing the first 10 xkcd comics ever published. 

```{r}
xkcd::xkcd_data
```



